---
title: "Homework 6"
author: "Zhenyu Zhou"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(skimr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

### Problem 2

Import dataset

```{r}
homicide_df = 
  read_csv("Data/homicide-data.csv") %>%
  mutate(
    city_state = str_c(city, ", ", state),
    solved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), FALSE, TRUE)
  ) %>%
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>%
  filter(!(city_state %in% c("Tulsa, AL"))) %>%
  filter(victim_race %in% c("White", "Black")) %>%
  mutate(
    victim_age = as.numeric(victim_age),
    victim_sex = as.factor(ifelse(victim_sex == "Unknown", NA, victim_sex)),
    victim_race = as.factor(victim_race)
  )
```

```{r}
fit_logistic = 
  homicide_df %>%
  filter(city == "Baltimore") %>%
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

fit_logistic %>%
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         ci_lower = exp(estimate - 1.96*std.error),
         ci_upper = exp(estimate + 1.96*std.error)) %>%
  filter(term == "victim_sexMale") %>% 
  select(term, log_OR = estimate, OR, ci_lower, ci_upper) %>%
  knitr::kable(digits = 3)
```

```{r}
glm_training = function(city_data){
  glm_model = glm(solved ~ victim_age + victim_sex + victim_race, data = city_data, family = binomial())
  glm_model %>%
    broom::tidy() %>%
    mutate(
      OR = exp(estimate),
      CI_lower = exp(estimate + qnorm(0.025) * std.error),
      CI_upper = exp(estimate + qnorm(0.975) * std.error)
    ) %>%
    filter(term == "victim_sexMale") %>%
    select(OR, CI_lower, CI_upper)
}
```

```{r}
cities_OR = 
  homicide_df %>%
  select(city_state:solved, victim_race:victim_sex) %>%
  nest(input_data = solved:victim_sex) %>%
  mutate(
    fit_logistic_city = purrr::map(input_data, glm_training)
  ) %>%
  select(city_state, fit_logistic_city) %>%
  unnest(fit_logistic_city)
```

```{r}
cities_OR %>%
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>%
  ggplot(aes(x = city_state,y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymax = CI_upper,ymin = CI_lower)) +
  labs(x = "City, State", y = "Adjusted Odds Ratio") + 
  theme(title = element_text(size = 8),
        axis.text.x = element_text(angle = 70, hjust = 1)
  )
```

In many cities, homicides with male victims are harder to solve than homicides with female victims. For example, most cities have estimated odds ratios below 1, indicating that homicides with male victims are more solved than homicides with female victims chances are lower.

### Problem 3

Load and clean the data

```{r, message = F}
bw_df = read_csv("./data/birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform))
```


```{r}
bw_df = bw_df %>% 
  select(-pnumlbw, -pnumsga)
```

There is no missing value in the current dataset. Since data entries for two variables pnumlbw and pnumsga are zero, we choose to drop these variables.

```{r}
bw_dfm = bw_df %>% 
  select(-parity, -malform, -smoken, -frace, -ppwt, -delwt)
```


Besides variables mentioned above, variables parity, malform, and smoken are highly skewed, thus I choose to remove the three variables. Variables ppwt and delwt are also removed considering mother's weight at delivery minus mother's weight before pregnancy equals the Variable wtgain. Based on the hypothesis that father's race is not significantly associated with brith weight, the predictor variables used in my model are `r names(bw_dfm)`. 

```{r}
bw_model = lm(bwt ~ ., data = bw_dfm)
summary(bw_model)
bw_newmodel = lm(bwt ~ babysex + bhead + blength + fincome + gaweeks + mheight + mrace + ppbmi + wtgain, data = bw_dfm)
```

The coefficients of variables menarche and momage are not significant at 0.1 significance level, so the R-sqaured is not impaired after dropping the two variables(`r summary(bw_model)$r.squared ` vs. `r summary(bw_newmodel)$r.squared `)

```{r}
bw_newmodel %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable()
```

```{r model residuals against fitted values}
bw_dfm %>% 
  add_residuals(bw_newmodel) %>% 
  add_predictions(bw_newmodel) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  stat_smooth(method = "lm")
```

```{r}
cv_df = 
  crossv_mc(bw_dfm, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(model_1  = map(train, ~lm(bwt ~ babysex + bhead + blength + fincome + 
                                     gaweeks + mheight + mrace + ppbmi + wtgain, data = .x)),
         model_2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model_3  = map(train, ~lm(bwt ~ blength*bhead*babysex, data = .x))) %>% 
  mutate(rmse_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))
```

```{r cross validation}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, color = model)) +
  geom_violin() +
  labs(x = "Model", y = "RMSE") 
```

Based on the violin plot, model 1 has the lowest level of prediction error probably due to the the large number of predictor variables. The best model is model 1.